Recurrent event analysis in the presence of real-time high frequency data via random subsampling

### 2020-06-22 write-up/fda-recurrent.tex
Fixing writeup

@@

\subsection{Bootstrap and multiple imputation under uncongenial }

@@

\subsection{Multiple sensors}

@@

During a XX month period in 2019, 91 psychiatric inpatients admitted for suicidal risk to Franciscan Children's Hospital  were enrolled in
 with histologically verified liver cirrhosis were recu
those presenting to a psychiatric hospital with suicide ideation
and/or a recent suicide attempt) during a high risk time period (i.e.,
post-hospitalization)

Currently, only 51 patients for whom the initial biopsy could be
reevaluated using more restrictive criteria were available for
analysis.
One of the goals of the study was to assess the association between sensor-based covariate information can used to identify distress early prior in the process of escalation by monitoring physiological correlates of distress -- in particular, electrodermal activity (EDA), a measure of skin conductance, and ``gACC'', a coordinate-free feature built from accelerometer data that measures physical movement. The scientific hypothesis to be tested is whether a spike in EDA and/or gACC

The goal of the sutyd

EDA and ACC sensor data along with buttonpress timestamps were
graciously provided by Evan Kleiman and his study team {\tt
https://kleimanlab.org}.
At the end of the study period, the mortality rate was 292/488, or
approximately 60\%.

The focus here is on two EDA and the  prothrombin index, a composite
blood coagulation index
related to liver function, measured initially at three-month intervals
and subsequently at roughly twelve-month intervals.
The individual prothrombin trajectories are highly variable,
both in forward and in reverse time,
which tends to obscure patterns and trends.
In Figure~\ref{fig:mean_traj}a the mean trajectory is plotted against time from recruitment
for two patient groups placebo/prednisone and censored/not censored.
Naturally, only those patients who are still alive are included in the average
for that time.
Figure~\ref{fig:mean_traj}b shows the same plots in reverse alignment.
While there are certain similarities in the two plots,
the differences in temporal trends are rather striking.
In particular, prothrombin levels in the six months prior to censoring are fairly stable,
which is in marked contrast with levels in the six months prior to failure,
as seen in the lower pair of curves.

Inspection of the graphs for uncensored patients in the right panel of Figure~\ref{fig:mean_traj} suggests
beginning with the simplest revival model in which the sequences
for distinct patients are independent Gaussian with moments

{\bf comparison over $\Delta$ and using imputation}

\subsection{Effect of electrodermal activity on prognosis}
Over a period of 5~years and one month following recruitment,
patient~$u$ had eight appointments with prothrombin values as follows:

>>>>

\subsection{Multiple sensors}
\label{section:multiplesensors}

@@

\subsubsection{Bootstrap and multiple imputation under uncongenial }

@@

@@

During a XX month period in 2019, 91 psychiatric inpatients admitted for suicidal risk to Franciscan Children's Hospital were enrolled in an observational study.  Study data were graciously provided by Evan Kleiman and his study team ({\tt https://kleimanlab.org}). Each study participant wore an Empatica E4~\cite{empaticae3}, a medical-grade wearable device that offers real-time physiological data.  One of the primary study goals was to assess the association between sensor-based physiological measurements and self-identified

can used to identify distress early prior in the process of escalation by monitoring physiological correlates of distress -- in particular, electrodermal activity (EDA), a measure of skin conductance, and ``gACC'', a coordinate-free feature built from accelerometer data that measures physical movement. The scientific hypothesis to be tested is whether a spike in EDA and/or gACC

To avoid, we focus on the study window 9AM to 8PM each study day.

At the end of the study period, the base rate of button pressing  rate was 292/488, or
approximately 60\%.

\begin{figure}[!th]
\caption{Button press distribution across study days (include number of people).}
\end{figure}

The focus here is on two EDA and the  prothrombin index, a composite
blood coagulation index
related to liver function, measured initially at three-month intervals
and subsequently at roughly twelve-month intervals.
The individual EDA and AI trajectories are highly variable, both in forward and when considering reverse time from event timepoints, which tends to obscure patterns and trends.  In Figure~XX, the mean trajectory is plotted against time from recruitment for two patient groups placebo/prednisone and censored/not censored. Naturally, only those patients who are still alive are included in the average
for that time.
Figure XX hows the same plots in reverse alignment.
While there are certain similarities in the two plots,
the differences in temporal trends are rather striking.
In particular, prothrombin levels in the six months prior to censoring are fairly stable,
which is in marked contrast with levels in the six months prior to failure,
as seen in the lower pair of curves.

\begin{figure}[!th]
\caption{EDA and ACC plots for average at non-event and event times.}
\end{figure}

Inspection of the graphs for uncensored patients in the right panel of Figure XX suggests beginning with the simplest revival model in which the sequences
for distinct patients are independent Gaussian with moments {\bf comparison over $\Delta$ and using imputation}

\begin{figure}[!th]
\caption{$\beta (t)$ for ACC and EDA with 95\% CI.}
\end{figure}

\subsection{Accounting for missing data and heterogeneity}

\subsection{Effect of electrodermal activity and activity index on moments of distress}

Over a period of 5~years and one month following recruitment,
patient~$u$ had eight appointments with prothrombin values as follows:
